The core transcriptome of mammalian placentas and the divergence of expression with placental shape

### 2016-12-06 manuscript/manuscript.Rnw
include 13 of 14 species listing
clarify most recent common ancestor listing
clarify pre-eclampsia onset

  \Sexpr{cpt.distribution.shape[,levels(`Min. Exp. in`)[2]]},

@@

The identification of multiple genes (\ac{CRH}, \ac{ADAM12},
\ac{KISS1}, \ac{PAPPA}, \ac{IL1RL1}, and \ac{PLAC1};
\cref{tab:human_lineage_specific}) which are associated with
pre-eclampsia which have increased expression on the \human lineage
may explain the larger proportion of pre-eclampsia observed in humans.
However, there are still genes which are associated with pre-eclampsia
which are also more highly expressed in the \mouse lineage such as
\ac{Afp} and \ac{Gjb2}. Furthermore, the onset of
pre-eclampsia is well before term; all of our placentas are term
placentas and provide limited information about the transcriptome
during the onset of pre-eclampsia.

@@

The core placenta transcriptome contains genes which are involved in
maternal-fetal tolerance, such as the annexins, and genes responsible
for cell-cell and cell-matrix interactions, such as \ac{LGALS1}.
These genes were almost certainly present in the placenta of the
common mammalian ancestor. We hypothesize that modifications to their
expression or function will compromise the development and
organization of the placenta.

>>>>

  \Sexpr{cpt.distribution.shape[,levels(`Min. Exp. in`)[2]]}, or
  \Sexpr{cpt.distribution.shape[,levels(`Min. Exp. in`)[3]]},

@@

The identification of multiple genes (\ac{CRH}, \ac{ADAM12},
\ac{KISS1}, \ac{PAPPA}, \ac{IL1RL1}, and \ac{PLAC1};
\cref{tab:human_lineage_specific}) which are associated with
pre-eclampsia which have increased expression on the \human lineage
may explain the larger proportion of pre-eclampsia observed in humans.
However, there are still genes which are associated with pre-eclampsia
which are also more highly expressed in the \mouse lineage such as
\ac{Afp} and \ac{Gjb2}. Furthermore, the biological processes which
ultimately result in pre-eclampsia occur well before term; all of our
placentas are term placentas and provide limited information about the
transcriptome during the onset of pre-eclampsia.

@@

The core placenta transcriptome contains genes which are involved in
maternal-fetal tolerance, such as the annexins, and genes responsible
for cell-cell and cell-matrix interactions, such as \ac{LGALS1}. These
genes were almost certainly present in the placenta of the most recent
common mammalian ancestor included in this study. We hypothesize that
modifications to their expression or function will compromise the
development and organization of the placenta.
